\documentclass{resume} % Use the custom resume.cls style
\usepackage[dvipsnames]{xcolor}
\usepackage{hyperref}
\usepackage[left=1in,top=1in,right=1in,bottom=1in]{geometry} % Document margins
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Franco Riottini Depetris} % Your name

\address{\\ Date of Birth: April 04, 1997 \\ Web: \url{https://francoriottini.github.io/}}

\address{\\ Phone: (+54 9) 342 5208 993 \\ Email: \texttt{friottinidepetris@udesa.edu.ar}, \texttt{friodep@umich.edu}}

\definecolor{CustomRed}{RGB}{196,18,48}

\renewenvironment{rSection}[1]{
\sectionskip
\textcolor{CustomRed}{\MakeUppercase{#1}}
\sectionlineskip
\hrule
\begin{list}{}{
\setlength{\leftmargin}{1.5em}
}
\item[]
}{
\end{list}
}

\begin{document}
\vspace{-0.3cm}
% Education
\begin{rSection}{Education}
{\bf University of Michigan} \hfill {\em 2025 - Present}
\\ PhD in Economics

{\bf Universidad de San Andres (UdeSA)} \hfill {\em 2024}
\\ MA in Economics
\\ GPA: 8/10 \textit{(10/32)} \hfill
\\ Thesis Grade: \textit{Outstanding} (Best Master's Thesis Award 2024). Supervision: Juan Carlos Hallak

{\bf Universidad Nacional del Litoral} \hfill {\em 2021}
\\ BA in Economics
\\ GPA: 7.67/10 \textit{(1/22)}
\\ BA in Applied Mathematics (not finished)
\\ GPA: 8/10
\hfill
\end{rSection}

\vspace{-0.3cm}
\begin{rSection}{Research Interests}
International economics, firm dynamics and productivity, education, applied econometrics, and machine learning.
\end{rSection}

\vspace{-0.3cm}
\begin{rSection}{Research Experience}
\begin{rSubsection}{PEC Consultant at IADB}{November 2022 - July 2025}{Supervisor: Christian Volpe Martincus}{}

\item Co-authored a forthcoming paper at ROIE using Large Language Models to accurately classify products under the Harmonized System Classification of International Trade.
\item Co-authored a working paper analyzing the heterogeneity of firms' performance in international trade when they are certified as organic.
\item Co-authored a working paper analyzing the consequences of trade in deforestation and other spillovers.
\item Provision of research assistance in projects in progress (together with projects co-authored with the World Bank).
\end{rSubsection}

\begin{rSubsection}{Predoctoral Research Assistant}{Jan 2023 - July 2025}{Universidad de San Andres (UdeSA)}{UdeSA}
\item Taught graduate and undergraduate courses and provided research assistance in projects in progress for Facundo Albornoz (Nottingham - UdeSA) and Francisco Roldan (IMF - UdeSA).
\end{rSubsection}

\begin{rSubsection}{Junior Research Associate}{March 2019 - March 2022}{Santa Fe's Chamber of Commerce, Research and Services Center}
\item Preparation of reports on the national and provincial economic situation, with special emphasis on international trade and agriculture. Database management and development. Application of the ARIMA X13 model for the regression of the time series necessary for the elaboration of the ICASFe. New Leaders Programme Coordinator (NDP)
\end{rSubsection}
\end{rSection}

\vspace{-0.3cm}
\begin{rSection}{Working Papers}
\begin{rSubsection}{Automatic Product Classification in International Trade: Machine Learning and Large Language Models}{2024}{Revise and Resubmit at Review of International Economics}
\item{Joint with Ignacio Marra de Artinano and Christian Volpe Martincus}
\end{rSubsection}

\begin{rSubsection}{Do Ambassadors Matter? The effect of ambassadors on trade promotion}{2024}{Revise and Resubmit at Economica}
\item{Master Thesis at Universidad de San Andres. Supervision: Juan Carlos Hallak.}
\item{Winner of Best Master's Thesis Award 2024}
\end{rSubsection}
\end{rSection}

\vspace{-0.3cm}
\begin{rSection}{Work in Progress}
\begin{rSubsection}{The Value of Organic Certifications}{2024}{}
\item{Joint with Ignacio Marra de Artinano, Gabriel Scattolo, Christian Volpe Martincus and Lucas Zavala}
\end{rSubsection}

\begin{rSubsection}{Trade and Deforestation: Evidence from Peru}{2024}{}
\item{Joint with Danielken Molina and Christian Volpe Martincus}
\end{rSubsection}
\end{rSection}

\vspace{-0.3cm}
\begin{rSection}{Teaching Experience}
\begin{rSubsection}{Lecturer}{March 2024 - July 2025}{Universidad de San Andres (UdeSA)}{}
\item Taught undergraduate courses in Introductory Economics.
\end{rSubsection}
\begin{rSubsection}{Teaching Assistant}{Aug 2022 - July 2025}{Universidad de San Andres (UdeSA)}{}
\item{Teaching assistant for courses including Quantitative Macroeconomics (graduate), International Trade, Introductory Mathematics and History of Economics Thought.}
\item{Guided student thesis projects in International Trade and Applied Microeconomics.}
\end{rSubsection}
\end{rSection}

\end{document}
